A New Metric for the Analysis of Swarms using Potential Fields

### 2018-08-05 paper.tex
More Updates

\title{A New Metric for the Analysis of Swarms that are modelled using potential fields}
\author{\uppercase{Neil Eliot}\authorrefmark{1},
\uppercase{David Kendall\authorrefmark{1}, and Michael Brockway\authorrefmark{1}}}
\address[1]{Northumbria University, Department of Computing and Information Sciences, 
Newcastle upon Tyne, NE1 8ST}

\markboth
{Eliot \headeretal: A New Metric for the Analysis of Swarms that are modelled using potential fields}
{Eliot \headeretal: A New Metric for the Analysis of Swarms that are modelled using potential fields}

>>>>

\title{A New Metric for the Analysis of Swarms using Potential Fields}
\author{\uppercase{Neil Eliot}\authorrefmark{1},
\uppercase{David Kendall\authorrefmark{1}, and Michael Brockway\authorrefmark{1}}}
\address[1]{Northumbria University, Department of Computing and Information Sciences, 
Newcastle upon Tyne, NE1 8ST}

\markboth
{Eliot \headeretal: A New Metric for the Analysis of Swarms using Potential Fields}
{Eliot \headeretal: A New Metric for the Analysis of Swarms using Potential Fields}
